A community-maintained standard library of population genetic simulations

### 2019-12-17 popSimManu.tex
clarified noise vs discrepancy

\stdpopsim allows us to readily compare these estimates to those drawn from a different
model of human history. In Figure \ref{fig:n_t_gutenkunst} we show estimates of
$N(t)$ from simulations using the same physical and genetic maps, but a different demographic
history -- that inferred by \cite{gutenkunst2009inferring}. Again we see that each
of the methods is capturing relevant parts of the population history, although the
degree of noise at any given time interval varies. In comparing inferences between the
models it is interesting to note that $N(t)$ estimates for the CHB and CEU
simulated samples are generally better across methods than estimates from the YRI simulations.

>>>>

\stdpopsim allows us to readily compare these estimates to those drawn from a different
model of human history. In Figure \ref{fig:n_t_gutenkunst} we show estimates of
$N(t)$ from simulations using the same physical and genetic maps, but a different demographic
history -- that inferred by \cite{gutenkunst2009inferring}. Again we see that each
of the methods is capturing relevant parts of the population history, although the
mismatch between simulated and inferred values varies over time. In comparing inferences between the
models it is interesting to note that $N(t)$ estimates for the CHB and CEU
simulated samples are generally better across methods than estimates from the YRI simulations.
